Quantum Magic Games

### 2023-07-04 paper/main.tex
paper => compatibility

\subsection{Formal Proof}
To prove that the quantum solution indeed works, we must demonstrate
two fundamental properties. First, the product of the outcomes of the
three measurements on each row (equivalently, column) is equal to 1
(equiv. -1). Second, the outcome of Alice's measurement on the
intersection is always equal to the outcome of
Bob's. Lemma~\ref{lem:product} formalizes the product property.

@@

\subsection{A Note on Simultaneous Measurements}
\label{sec:sim-meas}

@@

\textbf{TODO}

>>>>

\subsection{Formal Proof}\label{sec:msquare-proof}
To prove that the quantum solution indeed works, we must demonstrate
two fundamental properties. First, the product of the outcomes of the
three measurements on each row (equivalently, column) is equal to 1
(equiv. -1). Second, the outcome of Alice's measurement on the
intersection is always equal to the outcome of
Bob's. Lemma~\ref{lem:product} formalizes the product property.

@@

\subsection{A Note on Compatible Observables}
\label{sec:sim-meas}

As seen in the Section~\ref{sec:msquare-proof}, the operators on each
row and column are compatible. That is, for any row and any column,
the observables pairwise commute. This means that they can be
simultaneously diagonalized by the same eigenvectors. It turns out
that the simultaneous measurement of compatible operators is
equivalent to the measurement of a single nondegenerate
operator~\cite{peres:1997}. That is, instead of performing three
measurements, one for each cell, Alice and Bob could perform a single
measurement each, whose answers would tell them to which of the four
common eigenvectors their qubits would have collapsed to, had they
performed the individual measurements. Based on this, they could fill
each cell with the eigenvalue that corresponds to that eigenvector. To
construct these single measurements for each row and column, it
suffices to take the projectors onto the eigenvectors shared by the
observables. Example~\ref{ex:sim-meas} further illustrates this idea.

\begin{tcbexample}{Simultaneous Measurement}{sim-meas}
  Consider, for instance, the first row of the quantum solution for
  the magic square game, depicted in Figure~\ref{fig:quantum}. The
  observables in this row are \(I \otimes Z\), \(Z \otimes I\), and
  \(Z \otimes Z\). The eigenvectors common to these operators are
  \ket{00}, \ket{01}, \ket{10}, and \ket{11}. Alice, then, could
  simply construct an observable
  \[M = \ketbra{00}{00} + 2 \ketbra{01}{01} + 3 \ketbra{10}{10} + 4
    \ketbra{11}{11},\] which corresponds to the diagonal matrix
  \begin{equation*}
    M = \begin{pmatrix}
          1 & 0 & 0 & 0 \\
          0 & 2 & 0 & 0 \\
          0 & 0 & 3 & 0 \\
          0 & 0 & 0 & 4
    \end{pmatrix}.
  \end{equation*}
  By measuring \(M\) on her qubits, she would observe (with
  probability \(\nicefrac{1}{4}\)) the outcomes \(1\), \(2\), \(3\), or
  \(4\) , which uniquely identifies one of the four eigenvectors
  \ket{00}, \ket{01}, \ket{10}, or \ket{11}. Consequently, she would
  know the eigenvalues associated with the eigenvector ``observed'',
  and would be able to correctly fill the cells of the first row. For
  example, outcome \(3\) corresponds to \ket{10}. Hence, if she
  observes \(3\), she fills the first row with \(\{+1, -1, -1\}\).
\end{tcbexample}

@@
